### 2018-08-08 paper/approach.tex
up

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
\sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
source-bounded random walk (communication 
model),
\Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

@@

Further, \ac{SPOR} protocol (\cref{SPOR}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

A device's availability depends on its user's behavior, hence the device must 
predict this behavior.
This is best done jointly between all of the user's devices.
In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
allows the device \squad to act as an autonomous system.
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the \squad.

>>>>

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
\sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

@@

Further, \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

A device's availability depends on its user's behavior, hence the device must 
predict this behavior. This is best done jointly between all of the user's devices.
%In \cref{sec:squad_overlay}, we describe
Accordingly we introduce a protocol that allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

Finally, we introduce the complete \ac{SPORES} protocol, which 
allows the device \squad to act as an autonomous system (Figure~\ref{fig:outline} \ding{204}).
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the \squad.
